Experiences with Planning for Natural Language Generation

### 2009-06-03 trunk/Papers/ci-spark/experiments.tex
changes to section 4

We now turn our attention to a set of experiments arising from the GIVE domain.
Besides using some of the planners from the previous set of experiments (FF,
Metric-FF, and SGPLAN), we expand our testing to include the FF(h$_a$), LAMA, and
C$^3$ planners \todo{citations}. Each of these additional planners competed in the
deterministic ``sequential, satifying'' track of the 2008 International Planning
Competition; all planners generally performed well on the competition domains,
with LAMA the overall winner of the track.\footnote{See
\texttt{http://ipc.informatik.uni-freiburg.de/} for details of the 2008 IPC.}

@@

Preprocessing (parsing, grounding, etc.) time generally plays less of a role in
GIVE, compared with the sentence generation domain, however, its effects still
contribute significantly to the overall running time of a number of planners.
Figure~\ref{fig:give-minimal-grounding} shows the grounding time for FF, LAMA,
and SGPLAN on the minimal GIVE problems, compared with the total running time.
In the unordered variant of the minimal GIVE domain
(Figure~\ref{fig:give-minimal-grounding}(a)), the grounding time in LAMA and
SGPLAN accounts for a significant fraction of the total runtime: SGPLAN spends
around 40\% of its total runtime on preprocessing; for LAMA, this number
rises to at least 80\% for our test problems. For FF, the preprocessing time is
much less important than the search time, especially for large problem
instances. In the ordered case (Figure~\ref{fig:give-minimal-grounding}(b)), the
actual time spent on preprocessing is essentially unchanged from the unordered
case, and search time dominates the total runtime for all three planners.
However, FF is now much better at controlling the search,
compared with the unordered variant of the problem.

>>>>

We now turn our attention to a set of experiments arising from the GIVE domain.
Besides using many of the planners from the previous set of experiments (FF,
Metric-FF, and SGPLAN), we also expand our testing to include the FF(h$_a$)
\citep{keyder08:_ff_h_plann_for_plann}, LAMA \citep{richter08:_lama_plann}, and
C$^3$ \citep{lipovetzky08:_c3} planners. Each of these additional planners
competed in the deterministic ``sequential, satifying'' track of the 2008
International Planning Competition; all planners performed well on the
competition domains, with LAMA the overall winner of the track.\footnote{See
\texttt{http://ipc.informatik.uni-freiburg.de/} for details of the 2008 IPC.}

@@

Preprocessing (parsing, grounding, etc.) time generally plays less of a role in
GIVE, compared with the sentence generation domain, however, its effects still
contribute significantly to the overall running time of a number of planners.
Figure~\ref{fig:give-minimal-grounding} shows the grounding time for FF, LAMA,
and SGPLAN on the minimal GIVE problems, compared with the total running time.
In the unordered variant of the minimal GIVE domain
(Figure~\ref{fig:give-minimal-grounding}(a)), the grounding time in LAMA and
SGPLAN accounts for a significant fraction of the total runtime: SGPLAN spends
around 40\% of its total runtime on preprocessing; for LAMA, this number
rises to at least 80\% for our test problems. For FF, the preprocessing time is
much less important than the search time, especially for large problem
instances. In the ordered case (Figure~\ref{fig:give-minimal-grounding}(b)), the
actual time spent on preprocessing is essentially unchanged from the unordered
case, and search time dominates the total runtime for all three planners.
However, overall, FF is now much better at controlling the search, compared with
the other planners and its performance on the unordered variant of the problem.
